MSPMS Report

### 2024-05-21 inst/rmarkdown/templates/mspms_report/skeleton/skeleton.Rmd
updates to package structure.

```{r}
# The standard mspms data processing pipeline is used here. 
mspms = mspms::mspms(prepared_data,design_matrix,peptide_library,n_residues)
```

@@

```{r,fig.height = 8, fig.width = 10}
mspms::plot_heatmap(mspms)
```

@@

```{r,fig.height = 10, fig.width = 6}
print(mspms::plot_all_icelogos(mspms))
```

>>>>

```{r}
# The standard mspms data processing pipeline is used here. 
mspms = mspms::mspms(prepared_data,design_matrix)
```

@@

```{r}
mspms::plot_heatmap(mspms)
```

@@

```{r}
print(mspms::plot_all_icelogos(mspms))
```
